---
title: "Plotly examples"
output: 
  html_document:
    toc: true
    toc_float: true
---

Plotly helps build interactive dashboards using HTML, CSS, and other web-friendly platform. It does not work great with github documents. Java-script library as well as css are built in the background

You can access plotly from python and other things. We can do it directly from R without having to learn a new software

Plotly carries the same basic grammar of graphics idea in ggplot. Thought process of datase,t variables, and the type of plot

Interactive using plotly is great but we don't always need it. Think about the purpose of interactivity. It is handy to be able to interact with a plot such as zooming on specific groups or values or covey additional information that it's not obvious from color, size or shape 

Dashboards basically of products that show multiple interactive data in one place. If we need someone to interact with the data, it is helpful to create interactive dashboards. Basically a collection of plots arranged in some way

# Examples of plotly

```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

```{r}
data("nyc_airbnb")
```

